UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-08 files/paper/paper.tex
updates
update

\section{Method}

@@

>>>>

\section{Method}
Our approach

@@

\section{Experiments}

Here I want to show a number of things. First talk about the datasets used, Imagenet and the diving videos.
Second, show some general results. Explain how our network is able to do three very important things: 1) Restore an
image to its natural colors with varying amounts of distortion, i.e. blue hue, green hue, aka not just one type of
color distortion. 2) The network does not just subtract a certain hue from the entire image. Show how in the clownfish
image, part of the image has good colors, while part of it doesn't. Our network is able to leave correct colors. Third,
show that even images taken towards the water's surface, either above or below, are able to be restored correctly.

Third mention that since CycleGAN has a cycle consistent nature, compare their results. Then from there go into how
ours are better by showing results from Canny Edge Detector.
